### 2017-06-14 manuscript/manuscript.Rmd
OK so it's impossible to knitr::include_images from other folders. Shame.

```{r rstudio-git-1, fig.cap = "R Studio's Git tab for a newly created project."}
knitr::include_graphics("data/rstudio-git-1.png")
```

@@

```{r rstudio-git-2, fig.cap = "Creating a Git commit with R Studio."}
knitr::include_graphics("data/rstudio-git-2.png")
```

@@

[^git-version]: As of the writing of this article, the current version of Git is 2.13.1. 
# References

>>>>

```{r rstudio-git-1, fig.cap = "R Studio's Git tab for a newly created project."}
knitr::include_graphics("images/rstudio-git-1.png")
```

@@

```{r rstudio-git-2, fig.cap = "Creating a Git commit with R Studio."}
knitr::include_graphics("images/rstudio-git-2.png")
```

@@

[^git-version]: As of the writing of this article, the current version of Git is 2.13.1.

# References
